My title

### 2024-12-01 paper/paper.qmd
Updated appendix with structure of idealized survey and evaluation of dataset and moved tables to appendix

We use the statistical programming language R [@citeR].... Our data [@datahomicides].... Following @tellingstories, we consider...

@@

number_of_cases_victim_race |>
  ggplot(mapping = aes(x = victim_race, y = num_of_cases_victim_race)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Race", y = "Number of cases") +
  theme(legend.position = "bottom")
```
```{r}
#| label: tbl-victim-race-table
#| tbl-cap: "Number of homicide cases per sex in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

@@

## Surveys, sampling, and observational data (To be changed)

>>>>

We use the statistical programming language R [@citeR].... Our data [@datahomicides].... Following @citetellingstories, we consider...

@@

number_of_cases_victim_race |>
  ggplot(mapping = aes(x = victim_race, y = num_of_cases_victim_race)) +
  # Creates two graphs based on the status of the case
  facet_wrap(facets = vars(arrest_was_not_made), dir = "v") +
  geom_bar(stat = "identity", fill = "#a4ac86") +
  theme_minimal() +
  labs(x = "Victim's Race", y = "Number of cases") +
  theme(legend.position = "bottom")
```

```{r}
#| label: tbl-victim-race-table
#| tbl-cap: "Number of homicide cases per sex in New York and Los Angeles (2010 to 2017)"
#| echo: false
#| warning: false
#| message: false

@@

## Note on Reproducing

In order to reproduce the results in the paper, first run the 00-install_packages.R in the scripts folder located in this paper’s GitHub repository. Then run the other scripts based on the number at the beginning of the script name.

## Acknowledgments

We would like to thank @citetellingstories for providing assistance with the R code used to produce the tables and graphs in this paper.

## Code styling

Code written in the scripts was checked and styled with lintr [@citelintr] and styler [@citestyler].

## Additional Tables

\newpage
## Idealized Survey and Methodology {#subsec-ideal-survey}
- Link to literature

### Idealized Survey Objectives

### Sampling Approach

### Respondent Recruitment

### Data Validation

### Idealized Survey Design

### Link to Idealized Survey
- Using Google Forms

### Limitations

### Idealized Survey Questions
- Should have an introductory section and include details of a contact person
- Question type should be varied and appropriate.
- Have a final section that thank the respondents

\newpage 
## Overview and Evaluation of The Washington Post’s Dataset
- TODO: Make sure to link evaluation to literature

### Overview

### Sampling Approach
- what is the population, frame, and sample;
- how is the sample recruited;
- what sampling approach is taken, and what are some of the trade-offs of this; 
- how is non-response handled;

### Strengths and limitations
- what is good and bad about the sampling.
